---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearReg)
library(bench)
```

Since this is a package with functions deal with linear regression related problems, we can use a generated ramdom dataset to perform the example of usage. In real cases, the generated ramdom dataset could be replaced by any real dataset.
```{r}
x = rnorm(100)
x1 = rnorm(100)
x2 = rnorm(100)
Y = rnorm(100)
```

Note that, before using LinearReg Package to deal with , a x_matrix should be generated, which combine the independent(predict) variables as a matrix, each variable as a column.
```{r}
x_matrix = cbind(x, x1, x2)
```

Test for fit_simple_model:
```{r}
# This is how to solve a SLR model of y and A:
mod = fit_simple_model(y, x)
# And we could also solve it using the existed funtion lm() in R:
mod_lm = lm(y ~ x)

# Now we can compare the return values(the estimated coefficients) calculated through fit_simple_model() and the estimated coeffcients calculated through lm():
all.equal(mod, mod_lm$coefficients)
# We can also compare the efficiency through bench::mark():
efficiency = bench::mark(fit_simple_model(y, x),  lm(y ~ x)$coefficients,)
print(efficiency)
```





